My title\thanks{Code and data are available at: {[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}

### 2024-10-24 paper/paper.tex
Update Data Section in the Paper

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={First author; Yongqi Liu; Yuxuan Wei},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
{[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Yongqi Liu \and Yuxuan Wei}
\date{October 23, 2024}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#install.packages("tidymodels")}
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
-- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
v dplyr     1.1.4     v readr     2.1.5
v forcats   1.0.0     v stringr   1.5.1
v ggplot2   3.5.1     v tibble    3.2.1
v lubridate 1.9.3     v tidyr     1.3.1
v purrr     1.0.2     
-- Conflicts ------------------------------------------ tidyverse_conflicts() --
x dplyr::filter() masks stats::filter()
x dplyr::lag()    masks stats::lag()
i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(ggplot2)}
\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/02{-}analysis\_data/cleaned\_US\_voting.csv"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Rows: 1683 Columns: 11
-- Column specification --------------------------------------------------------
Delimiter: ","
chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
dbl  (4): numeric_grade, sample_size, percent, transparency_score
date (2): start_date, end_date

i Use `spec()` to retrieve the full column specification for this data.
i Specify the column types or set `show_col_types = FALSE` to quiet this message.
\end{verbatim}

@@

We use the statistical programming language R (R Core Team 2023)\ldots.
Following Alexander (2023), we consider\ldots{}

Overview text

\subsection{Measurement}\label{measurement}

Some paragraphs about how we go from a phenomena in the world to an
entry in the dataset.

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

Some of our data is of penguins (\textbf{?@fig-bills}),

Talk more about it.

And also planes (\textbf{?@fig-planes}). (You can change the height and
width, but don't worry about doing that until you have finished every
other aspect of the paper - Quarto will try to make it look nice and the
defaults usually work well once you have enough text.)

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine
a few into one if they go together naturally.

@@

To model Donald Trump's polling percentages over time, we employed a
Bayesian linear regression framework. Bayesian methods provide a
flexible approach to inference by incorporating prior beliefs and
updating them with observed data, allowing us to quantify uncertainty in
both parameter estimates and predictions.

Here we briefly describe the Bayesian model used to investigate the
winning probability of Trump. Background details and diagnostics are
included in Appendix~\ref{sec-model-details}.

@@

The model takes the form: The model takes the form:

\section{\#Interpretation of
Coefficients:}\label{interpretation-of-coefficients}

@@

The posterior distributions of the parameters allow us to quantify the
uncertainty around each effect: - The coefficient for end\_date informs
us about how Trump's polling percentages have evolved over time. A
positive coefficient would suggest an upward trend, while a negative
coefficient would indicate a decline. - The coefficient for
numeric\_grade captures the impact of pollster quality on the polling
percentage. High-quality pollsters may produce different estimates
compared to lower-quality ones. - The state-level effects account for
regional differences in Trump's support. Some states may show
significantly higher or lower levels of support, even after adjusting
for the time of the poll and pollster quality.

@@

\includegraphics{paper_files/figure-pdf/fig-diagnosis-1.pdf}

@@

\caption{\label{fig-diagnosis}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(car)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: carData
\end{verbatim}

\begin{verbatim}

Attaching package: 'car'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:dplyr':

    recode
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:purrr':

    some
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{vif}\NormalTok{(regression\_model)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
                       GVIF Df GVIF^(1/(2*Df))
numeric_grade      1.294110  1        1.137590
sample_size        1.289750  1        1.135672
state              2.082151 44        1.008369
transparency_score 1.263558  1        1.124081
end_date           1.309491  1        1.144330
\end{verbatim}

@@

\section{Appendix B: Idealized Methodology and
Survey}\label{appendix-b-idealized-methodology-and-survey}

@@

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-tellingstories}
Alexander, Rohan. 2023. \emph{Telling Stories with Data}. Chapman;
Hall/CRC. \url{https://tellingstorieswithdata.com/}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

>>>>

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Xuanle Zhou; Yongqi Liu; Yuxuan Wei},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
{[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Xuanle Zhou \and Yongqi Liu \and Yuxuan Wei}
\date{October 23, 2024}

@@

@@

This study uses R packages (R Core Team 2023) to clean and analyz the
dataset , including libraries from tidyverse {[}{]}, ggplot2{[}{]}.

After cleaning the data, which included grouping and removing missing
values, the analysis dataset consists of 1,683 observations, focusing on
the following 11 variables: pollster name, methodology, numeric grade,
start date, end date, sample size, candidate name, percentage,
transparency score, and population group.

\subsection{Data Measurement and
Considerations}\label{data-measurement-and-considerations}

The dataset for this analysis is sourced from FiveThirtyEight, which
rigorously collects and aggregates polling data from a variety of firms
to reflect public opinion. To ensure the integrity of the data, only
polls that adhere to specific criteria are included in the dataset. Each
poll must provide essential information, such as the pollster's name,
survey dates, sample sizes, and methodological details (e.g., polling
medium, voter files, weighting criteria). Polls that are deemed
nonscientific, that blend data from multiple sources, or that are
conducted by hobbyists are excluded.

Once a poll meets these stringent standards, it is incorporated into the
database, enabling it to inform polling averages, forecasts, and
political coverage. This careful selection process ensures that the
dataset accurately captures and reflects the nuances of public sentiment
and behavior.

@@

The outcome variable of interest for this research is the percentage,
representing the level of public support for Donald Trump. The
distribution in Figure~\ref{fig-pct} indicates that most observations
cluster around a support percentage of approximately 48\%, suggesting
moderate backing from the electorate. Additionally, a smaller proportion
of polls show support exceeding 55\%, indicating that while Trump has a
core base, many voters remain either indifferent or opposed to him.

\includegraphics{paper_files/figure-pdf/fig-pct-1.pdf}

\caption{\label{fig-pct}Distribution of Support (percent) for Donald
Trump}

@@

\subsubsection{Numeric Grade}\label{numeric-grade}

The numeric grade reflects the quality of the pollster, with
FiveThirtyEight defining a scale from 0 to 3. A grade of 0 indicates a
low-quality poll, while a grade of 3 signifies a high-quality pollster.
After filtering for pollsters with a numeric grade higher than 2.5, we
identified a total of 30 distinct pollsters, with half of them scoring
between 2.6 and 2.8, as shown in Figure~\ref{fig-numeric-grade} .

\includegraphics{paper_files/figure-pdf/fig-numeric-grade-1.pdf}

\caption{\label{fig-numeric-grade}Distribution of Numeric Grades (2.6 to
3.0)}

\subsubsection{Sample Size}\label{sample-size}

The sample size indicates the number of respondents in each poll. The
distribution in Figure~\ref{fig-sample-size} exhibits a right-skewed
shape, suggesting that there are more observations with smaller sample
sizes compared to larger ones. The peak of the distribution is around
1,000, indicating that this is the most common sample size used in the
polls. Overall, the sample size data highlights that each poll contains
a sufficient number of respondents to provide reliable insights.

\includegraphics{paper_files/figure-pdf/fig-sample-size-1.pdf}

\caption{\label{fig-sample-size}Distribution of Sample Size}

\subsubsection{Transparency Score}\label{transparency-score}

The Transparency Score measures how transparent a pollster is,
calculated based on the amount of information disclosed about its polls,
weighted by recency. The highest possible score is 10, while the lowest
is 0. The distribution of Transparency Scores for the filtered pollsters
shows a peak around 9 as presented in
Figure~\ref{fig-transparency-score}, indicating that this is the most
common score. This suggests that among the selected pollsters, there is
a predominance of high transparency scores.

\includegraphics{paper_files/figure-pdf/fig-transparency-score-1.pdf}

\caption{\label{fig-transparency-score}Distribution of Transparency
Score}

\subsubsection{end date}\label{end-date}

The end date indicates when each poll concluded.
Figure~\ref{fig-end-date} shows that as the final result of the U.S.
election approached, more polls were conducted and completed. This trend
reflects an increased interest in capturing public opinion and
predicting electoral outcomes as election day neared, emphasizing the
significance of real-time sentiment analysis during this critical
period.

\includegraphics{paper_files/figure-pdf/fig-end-date-1.pdf}

\caption{\label{fig-end-date}Distribution of End Dates}

@@

To model Donald Trump's polling percentages over time, we employed a
multiple linear regression framework. This approach estimates the
relationship between polling percentages and various predictors by
fitting a linear equation to the data. By analyzing the coefficients, we
can quantify the impact of each predictor on Trump's polling
percentages, while also assessing the overall fit of the model and
making predictions based on the observed trends.

Here we briefly describe the multiple linear regression model used to
investigate the winning probability of Trump. Background details and
diagnostics are included in Appendix~\ref{sec-model-details}.

@@

The model takes the form:

\begin{align}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
\epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align}

Where: \begin{align}
\beta_0 & \text{ is the intercept term} \\
\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
\sigma^2 & \text{ is the variance of the error term}
\end{align}

\section{Interpretation of
Coefficients:}\label{interpretation-of-coefficients}

@@

The posterior distributions of the parameters allow us to quantify the
uncertainty around each effect:\\

\begin{itemize}
\tightlist
\item
  The coefficient for end\_date informs us about how Trump's polling
  percentages have evolved over time. A positive coefficient would
  suggest an upward trend, while a negative coefficient would indicate a
  decline.\\
\item
  The coefficient for numeric\_grade captures the impact of pollster
  quality on the polling percentage. High-quality pollsters may produce
  different estimates compared to lower-quality ones.\\
\item
  The state-level effects account for regional differences in Trump's
  support. Some states may show significantly higher or lower levels of
  support, even after adjusting for the time of the poll and pollster
  quality.
\end{itemize}

@@

\includegraphics{paper_files/figure-pdf/fig-diagnosis-1-1.pdf}

@@

\caption{\label{fig-diagnosis-1}}

@@

@@

\textless\textless\textless\textless\textless\textless\textless{}
Updated upstream \# Appendix B: Idealized Methodology and Survey

@@

\section{\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{}
7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4}\label{bdf4d96b1910dc96b7cd995f3c7eccd50b162f4}

\section{Idealized Methodology and
Survey}\label{idealized-methodology-and-survey}

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
Stashed changes
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.
